\textbf{Supplementary Information}

### 2020-11-16 submission/supplementary.Rmd
Coauthors review done.

\linenumbers
\sisetup{mode=text}
\setlength\parindent{24pt}

@@

```{r out.width="80%", fig.align="center", fig.cap="Rarefaction curves of bacterial and archaeal communities from the surfaces of two marine macrophytes (\\textit{C. nodosa} and \\textit{C. cylindracea}) sampled in the Bay of Saline and the Bay of Funtana (Mixed and Monospecific Settlements) in two contrasting seasons (4 December 2017 and 19 June 2018).\\label{rarefaction}", fig.pos="H"}
include_graphics("../results/figures/rarefaction.jpg")
```

>>>>

[]: # (\linenumbers)
\sisetup{mode=text}
\setlength\parindent{24pt}

@@

```{r out.width="80%", fig.align="center", fig.cap="Rarefaction curves of bacterial and archaeal communities from the surfaces of two marine macrophytes (\\textit{C. nodosa} and \\textit{C. cylindracea}) sampled in the Bay of Saline and the Bay of Funtana (mixed and monospecific settlements) in two contrasting seasons (4 December 2017 and 19 June 2018).\\label{rarefaction}", fig.pos="H"}
include_graphics("../results/figures/rarefaction.jpg")
```

### 2020-11-16 submission/supplementary.tex
Coauthors review done.

\linenumbers
\sisetup{mode=text}
\setlength\parindent{24pt}

@@

\caption{Rarefaction curves of bacterial and archaeal communities from the surfaces of two marine macrophytes (\textit{C. nodosa} and \textit{C. cylindracea}) sampled in the Bay of Saline and the Bay of Funtana (Mixed and Monospecific Settlements) in two contrasting seasons (4 December 2017 and 19 June 2018).\label{rarefaction}}\label{fig:unnamed-chunk-1}
\end{figure}

>>>>

\sisetup{mode=text}
\setlength\parindent{24pt}

@@

\caption{Rarefaction curves of bacterial and archaeal communities from the surfaces of two marine macrophytes (\textit{C. nodosa} and \textit{C. cylindracea}) sampled in the Bay of Saline and the Bay of Funtana (mixed and monospecific settlements) in two contrasting seasons (4 December 2017 and 19 June 2018).\label{rarefaction}}\label{fig:unnamed-chunk-1}
\end{figure}
